---
title: "Evaluate performance of multivariate BMAseq, voom, limma, edgeR, and DESeq2 on inferring differentially expressed genes"
author: "Anni Liu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



### Save and load images
```{r eval=FALSE}
image.date <- format(Sys.Date(), "%Y%b%d")
save.image(file = paste0("../ApplicationData/derived/", image.date, "_image_RData"))
```

```{r}
load("../ApplicationData/derived/2022Dec24_image_RData")
```


## Load original data
```{r}
# Attach the package
suppressPackageStartupMessages(easypackages::libraries("BMAseq", "limma", "qvalue", "parallel", "ggVennDiagram", "gridExtra", "tidyverse"))

dat.expr <- dget("../ApplicationData/derived/dat.expr.Subcutaneous") 
dat.pheno <- dget("../ApplicationData/derived/dat.pheno.Subcutaneous") 

dim(dat.expr) # 24660 genes and 404 subjects
dim(dat.pheno) # 404 subjects and 13 phenotypes

dat.pheno[1:5, ]
dat.expr[1:5, 1:5]
```

```{r filter}
# Pre-filter the genes
# Here we perform the median absolute deviation with the threshold of 0.8 to select genes that are most likely to distinguish the samples
dat.expr.new <- dat.expr[apply(dat.expr, 1, function(x) mad(x) > 0.8), ] # We have 24455 genes
```


## Random data segmentation
```{r random.divide}
# Randomly divide the datasets into 50% training and 50% test sets
# Check the distribution of binary phenotypes
sapply(names(dat.pheno), function(x) with(dat.pheno, table(get(x))) )  

set.seed(190987)
test.ind <- sample(1:nrow(dat.pheno), ceiling(0.5*nrow(dat.pheno)))
dat.pheno.train <- dat.pheno[-test.ind, ]
dat.pheno.test <- dat.pheno[test.ind, ]
sapply(names(dat.pheno.train), function(x) with(dat.pheno.train, table(get(x))) )
sapply(names(dat.pheno.test), function(x) with(dat.pheno.test, table(get(x))) )  

dat.expr.train <- dat.expr.new[, rownames(dat.pheno.train)]
dat.expr.test <- dat.expr.new[, rownames(dat.pheno.test)]
```


## Multivariate analysis without interaction

### One-step way of `BMAseq.multi`
```{r multi.noTMM}
vars.pool <- c("BMI", "AGE", "SEX", "MHABNWBC") 
# We select these four variables because they show the highest number of common DEGs identified by BMAseq between the training set and testing set 

t0 <- Sys.time()
output.multi.train <- BMAseq.multi(dat.expr.counts = dat.expr.train,  # ALiu: incorporate multi.core
                                   dat.pheno = dat.pheno.train, 
                                   var.pool = vars.pool, 
                                   max.nvar = 4, 
                                   interaction = NULL, 
                                   cut.BF = 1, 
                                   cut.FDR = 0.05)
t1 <- Sys.time()
t1 - t0
# Time difference of 5.316691 mins

output.multi.test <- BMAseq.multi(dat.expr.counts = dat.expr.test, 
                                  dat.pheno = dat.pheno.test, 
                                  var.pool = vars.pool, 
                                  max.nvar = 4, 
                                  interaction = NULL, 
                                  cut.BF = 1, 
                                  cut.FDR = 0.05)
```

```{r multi.logcpm}
dim(output.multi.train$dat.expr.logcpm)
output.multi.train$dat.expr.logcpm[1:5, 1:5]

dim(output.multi.test$dat.expr.logcpm)
output.multi.test$dat.expr.logcpm[1:5, 1:5]
```

```{r multi.weight}
dim(output.multi.train$weights)
output.multi.train$weights[1:5, 1:5]

dim(output.multi.test$weights)
output.multi.test$weights[1:5, 1:5]
```

```{r multi.pheno}
dim(output.multi.train$dat.pheno.new)
output.multi.train$dat.pheno.new[1:5, ]

dim(output.multi.test$dat.pheno.new)
output.multi.test$dat.pheno.new[1:5, ]
```

```{r multi.modelspace}
length(output.multi.train$model.space)
output.multi.train$model.space

length(output.multi.train$model.space)
output.multi.train$model.space
```

```{r multi.postmodelprob}
dim(output.multi.train$post.modelprob)
output.multi.train$post.modelprob[1:5, 1:5]

dim(output.multi.test$post.modelprob)
output.multi.test$post.modelprob[1:5, 1:5]
```

```{r multi.postinclmodelprob.main}
dim(output.multi.train$post.incl.modelprob.Main)
output.multi.train$post.incl.modelprob.Main[1:5, ]

dim(output.multi.test$post.incl.modelprob.Main)
output.multi.test$post.incl.modelprob.Main[1:5, ]
```

```{r multi.bestmodel.DEG}
length(output.multi.train$bestmodel.DEG.Main)
dim(output.multi.train$bestmodel.DEG.Main$BMI$`~1+BMI+AGE`)
dim(output.multi.train$bestmodel.DEG.Main$AGE$`~1+BMI+AGE`)
setdiff(output.multi.train$bestmodel.DEG.Main$BMI$`~1+BMI+AGE`, 
        output.multi.train$bestmodel.DEG.Main$AGE$`~1+BMI+AGE`)

# Extract the top 1 DE gene for each best model corresponding to each variable of interest
top1.train <- mclapply(1:length(output.multi.train$bestmodel.DEG.Main),
                       function(i) mclapply(1:length(output.multi.train$bestmodel.DEG.Main[[i]]),
                                            function(j) output.multi.train$bestmodel.DEG.Main[[i]][[j]][1, ], 
                                            mc.cores = 10L),
                       mc.cores = 10L)

# Recursively rename the list element 
names(top1.train) = vars.pool
for (i in 1:length(top1.train)) {
  names(top1.train[[i]]) = names(output.multi.train[["bestmodel.DEG.Main"]][[i]])
}

# Show the top1 DE gene for each best model corresponding to each variable of interest
top1.train

# Repeat the above steps for the testing set
length(output.multi.test$bestmodel.DEG.Main)

top1.test <- mclapply(1:length(output.multi.test$bestmodel.DEG.Main),
                      function(i) mclapply(1:length(output.multi.test$bestmodel.DEG.Main[[i]]),
                                           function(j) output.multi.test$bestmodel.DEG.Main[[i]][[j]][1, ], 
                                           mc.cores = 10L),
                      mc.cores = 10L)

names(top1.test) = vars.pool
for (i in 1:length(top1.test)) {
  names(top1.test[[i]]) = names(output.multi.test[["bestmodel.DEG.Main"]][[i]])
}

top1.test
```

```{r multi.bestmodel.DEG.compare.withinBMAseq.noTMM}
# Not consider the specific model formula
ENSG.res.train.all <- unlist(output.multi.train[["bestmodel.DEG.Main"]])[grep("ENSG", unlist(output.multi.train[["bestmodel.DEG.Main"]]))]
ENSG.res.test.all <- unlist(output.multi.test[["bestmodel.DEG.Main"]])[grep("ENSG", unlist(output.multi.test[["bestmodel.DEG.Main"]]))]

# Display the common DEGs between the training set and testing set identified by multivariate BMAseq
ggVennDiagram(list(Train = ENSG.res.train.all, Test = ENSG.res.test.all), 
              label_alpha = 0, label_color = "white") + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5, colour = "red")) + 
  ggtitle("Common DEGs identified by multivariate BMAseq")
```


### Two-step way of `BMAseq.multi.postprob` and `BMAseq.multi.DEG`
```{r multi.twoway.noTMM}
t0 <- Sys.time()
output.multi.train.s1 <- BMAseq.multi.postprob(dat.expr.counts = dat.expr.train,
                                               dat.pheno = dat.pheno.train, 
                                               var.pool = vars.pool, 
                                               max.nvar = 4, 
                                               interaction = NULL, 
                                               cut.BF = 1)
output.multi.train.s2 <- BMAseq.multi.DEG(dat.pheno = output.multi.train.s1$dat.pheno.new, 
                                          model.space = output.multi.train.s1$model.space, 
                                          post.modelprob = output.multi.train.s1$post.modelprob, 
                                          var.pool = vars.pool, 
                                          interact = F, 
                                          cut.FDR = 0.05)
t1 <- Sys.time()
t1 - t0


# Repeat the above steps for the testing set
output.multi.test.s1 <- BMAseq.multi.postprob(dat.expr.counts = dat.expr.test,  
                                              dat.pheno = dat.pheno.test, 
                                              var.pool = vars.pool, 
                                              max.nvar = 4, 
                                              interaction = NULL, 
                                              cut.BF = 1)

output.multi.test.s2 <- BMAseq.multi.DEG(dat.pheno = output.multi.test.s1$dat.pheno.new, 
                                         model.space = output.multi.test.s1$model.space, 
                                         post.modelprob = output.multi.test.s1$post.modelprob, 
                                         var.pool = vars.pool, 
                                         interact = F, 
                                         cut.FDR = 0.05)
```

```{r logcpm.multiBMAseq}
dim(output.multi.train.s1$dat.expr.logcpm)
output.multi.train.s1$dat.expr.logcpm[1:5, 1:5]

dim(output.multi.test.s1$dat.expr.logcpm)
output.multi.test.s1$dat.expr.logcpm[1:5, 1:5]
```

```{r weight.multiBMAseq}
dim(output.multi.train.s1$weights)
output.multi.train.s1$weights[1:5, 1:5]

dim(output.multi.test.s1$weights)
output.multi.test.s1$weights[1:5, 1:5]
```

```{r pheno.multiBMAseq}
dim(output.multi.train.s1$dat.pheno.new)
output.multi.train.s1$dat.pheno.new[1:5, ]

dim(output.multi.test.s1$dat.pheno.new)
output.multi.test.s1$dat.pheno.new[1:5, ]
```

```{r modelspace.multiBMAseq}
length(output.multi.train.s1$model.space)
output.multi.train.s1$model.space

length(output.multi.test.s1$model.space)
output.multi.test.s1$model.space
```

```{r postmodelprob.multiBMAseq}
dim(output.multi.train.s1$post.modelprob)
output.multi.train.s1$post.modelprob[1:5, 1:5]

dim(output.multi.test.s1$post.modelprob)
output.multi.test.s1$post.modelprob[1:5, 1:5]
```

```{r postinclmodelprobMain.multiBMAseq}
dim(output.multi.train.s2$post.incl.modelprob.Main)
output.multi.train.s2$post.incl.modelprob.Main[1:5, ]

dim(output.multi.test.s2$post.incl.modelprob.Main)
output.multi.test.s2$post.incl.modelprob.Main[1:5, ]
```

```{r eFDRMain.noTMM}
dim(output.multi.train.s2$eFDR.Main)
output.multi.train.s2$eFDR.Main[1:5, ]

dim(output.multi.test.s2$eFDR.Main)
output.multi.test.s2$eFDR.Main[1:5, ]
```

```{r indicatoreFDRMain.noTMM}
dim(output.multi.train.s2$indicator.eFDR.Main)
output.multi.train.s2$indicator.eFDR.Main[1:5, ]

dim(output.multi.test.s2$indicator.eFDR.Main)
output.multi.test.s2$indicator.eFDR.Main[1:5, ]

# Number of DE genes associated with the main effect of BMI
# sum(output.multi.train.s2$indicator.eFDR.Main[, 1] == 1)
# [1] 2027
# sum(output.multi.test.s2$indicator.eFDR.Main[, 1] == 1)
# [1] 175
```

```{r summary.multiBMAseq}
output.multi.train.s2$summary.nDEG
output.multi.test.s2$summary.nDEG
```

```{r DEGbestmodelMain.multiBMAseq}
output.multi.train.s2$DEG.bestmodel.Main
output.multi.test.s2$DEG.bestmodel.Main

# dim(output.multi.train.s2$DEG.bestmodel.Main$BMI) # 2027    3
```

```{r bestmodelDEGMain.multiBMAseq}
output.multi.train.s2$bestmodel.DEG.Main
output.multi.test.s2$bestmodel.DEG.Main
```


#### Common DE genes between the training set and testing set identified by each approach
##### multiBMAseq
```{r DEG.compare.within.MultiBMAseq.noTMM}
multiBMAseq.DEG.ENSG.train <- mclapply(1:4,
                                       function(i) {names(which(output.multi.train.s2$indicator.eFDR.Main[, i] == 1)) },
                                       mc.cores = 4L)
multiBMAseq.DEG.ENSG.test <- mclapply(1:4,
                                      function(i) {names(which(output.multi.test.s2$indicator.eFDR.Main[, i] == 1)) },
                                      mc.cores = 4L)
names(multiBMAseq.DEG.ENSG.train) = names(multiBMAseq.DEG.ENSG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate BMAseq
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = multiBMAseq.DEG.ENSG.train[[x]], 
                                                          Test = multiBMAseq.DEG.ENSG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x])},
              mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### multiBMAseq + TMM
```{r DEG.compare.within.MultiBMAseq.TMM}
source("BMAseq.multi.postprob.norm.R")
source("Bayesfactor.R")
t0 <- Sys.time()
output.multi.train.s1 <- BMAseq.multi.postprob.norm(dat.expr.counts = dat.expr.train,  
                                                    dat.pheno = dat.pheno.train, 
                                                    var.pool = vars.pool, 
                                                    max.nvar = 4, 
                                                    interaction = NULL, 
                                                    cut.BF = 1)
output.multi.train.s2 <- BMAseq.multi.DEG(dat.pheno = output.multi.train.s1$dat.pheno.new, 
                                          model.space = output.multi.train.s1$model.space, 
                                          post.modelprob = output.multi.train.s1$post.modelprob, 
                                          var.pool = vars.pool, 
                                          interact = F, 
                                          cut.FDR = 0.05)
t1 <- Sys.time()
t1 - t0


# Repeat the above steps for the testing set
output.multi.test.s1 <- BMAseq.multi.postprob.norm(dat.expr.counts = dat.expr.test, 
                                                   dat.pheno = dat.pheno.test, 
                                                   var.pool = vars.pool, 
                                                   max.nvar = 4, 
                                                   interaction = NULL, 
                                                   cut.BF = 1)

output.multi.test.s2 <- BMAseq.multi.DEG(dat.pheno = output.multi.test.s1$dat.pheno.new, 
                                         model.space = output.multi.test.s1$model.space, 
                                         post.modelprob = output.multi.test.s1$post.modelprob, 
                                         var.pool = vars.pool, 
                                         interact = F, 
                                         cut.FDR = 0.05)

multiBMAseq.DEG.ENSG.train <- mclapply(1:4,
                                       function(i) {names(which(output.multi.train.s2$indicator.eFDR.Main[, i] == 1)) },
                                       mc.cores = 4L)
multiBMAseq.DEG.ENSG.test <- mclapply(1:4,
                                      function(i) {names(which(output.multi.test.s2$indicator.eFDR.Main[, i] == 1)) },
                                      mc.cores = 4L)
names(multiBMAseq.DEG.ENSG.train) = names(multiBMAseq.DEG.ENSG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate BMAseq
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = multiBMAseq.DEG.ENSG.train[[x]], 
                                                          Test = multiBMAseq.DEG.ENSG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x])},
              mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### voom + limma (full model)
```{r DEG.compare.within.Multivoom_limma.fullmodel.noTMM}
# Set the model design matrix for each variable of interest for the training and testing sets, respectively
design.train <- model.matrix(~BMI + AGE + SEX + MHABNWBC, data = dat.pheno.train)
design.test <- model.matrix(~BMI + AGE + SEX + MHABNWBC, data = dat.pheno.test)

# Estimate the voom weights for each model design mapping to each variable of interest
voom.train <- voom(dat.expr.train,
                   design = design.train,
                   lib.size = colSums(dat.expr.train))

# Fit the linear model with the voom weights
voom.fit.train <- lmFit(voom.train[["E"]],
                        design = design.train,
                        weights = voom.train[["weights"]])

# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) {
                         t <- voom.fit.train[["coefficients"]][, i+1]/voom.fit.train[["stdev.unscaled"]][, i+1]/voom.fit.train[["sigma"]] # 1: intercept
                         p <- 2*pt(-abs(t), df = voom.fit.train[["df.residual"]])
                         return(qvalue(p)) },
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
voom.DEG.train <- mclapply(1:4,
                           function(i) rownames(dat.expr.train)[ eFDR.train[[i]][["qvalues"]] < 0.05 ],
                           mc.cores = 4L)

# Name elements using the corresponding variable of interest for all list objects of model design, voom weight, model fit, eFDR, and DEG ID
names(eFDR.train) = names(voom.DEG.train) = vars.pool 

# Repeat the above steps for the testing data
voom.test <- voom(dat.expr.test,
                  design = design.test,
                  lib.size = colSums(dat.expr.test))

voom.fit.test <- lmFit(voom.test[["E"]],
                       design = design.test,
                       weights = voom.test[["weights"]])

eFDR.test <- mclapply(1:4,
                      function(i) {
                        t <- voom.fit.test[["coefficients"]][, i+1]/voom.fit.test[["stdev.unscaled"]][, i+1]/voom.fit.test[["sigma"]] # 1: intercept
                        p <- 2*pt(-abs(t), df = voom.fit.test[["df.residual"]])
                        return(qvalue(p)) },
                      mc.cores = 4L)

voom.DEG.test <- mclapply(1:4,
                          function(i) rownames(dat.expr.test)[ eFDR.test[[i]][["qvalues"]] < 0.05 ],
                          mc.cores = 4L)

names(eFDR.test) = names(voom.DEG.test) = vars.pool 

# Display the common DEGs between the training set and testing set identified by multivariate limma with voom weights
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = voom.DEG.train[[x]], Test = voom.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))

# BMI
# length(voom.DEG.train[[1]])
# [1] 4739
# length(voom.DEG.test[[1]])
# [1] 111
```


##### voom + limma + TMM (full model)
```{r DEG.compare.withi,nMultivoom_limma.fullmodel.TMM}
# Set the model design matrix for the training and testing sets, respectively
design.train <- model.matrix(~BMI + AGE + SEX + MHABNWBC, data = dat.pheno.train)
design.test <- model.matrix(~BMI + AGE + SEX + MHABNWBC, data = dat.pheno.test)

# Estimate the voom weights for the model design
voom.train <- voom(counts = dat.expr.train,
                   design = design.train,
                   lib.size = colSums(dat.expr.train)*calcNormFactors(dat.expr.train, lib.size = colSums(dat.expr.train))) # Use TMM normalization factor to transform the original library size into the effective library size

# Fit the linear model with the voom weights
voom.fit.train <- lmFit(voom.train[["E"]],
                        design = design.train,
                        weights = voom.train[["weights"]])

# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) {
                         t <- voom.fit.train[["coefficients"]][, i+1]/voom.fit.train[["stdev.unscaled"]][, i+1]/voom.fit.train[["sigma"]] # 1: intercept
                         p <- 2*pt(-abs(t), df = voom.fit.train[["df.residual"]])
                         return(qvalue(p)) },
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
voom.DEG.train <- mclapply(1:4,
                           function(i) rownames(dat.expr.train)[ eFDR.train[[i]][["qvalues"]] < 0.05 ],
                           mc.cores = 4L)

# Name elements using the corresponding variable of interest for all list objects of model design, voom weight, model fit, eFDR, and DEG ID
names(eFDR.train) = names(voom.DEG.train) = vars.pool 

# Repeat the above steps for the testing data
voom.test <- voom(counts = dat.expr.test,
                  design = design.test,
                  lib.size = colSums(dat.expr.test)*calcNormFactors(dat.expr.test, lib.size = colSums(dat.expr.test)))

voom.fit.test <- lmFit(voom.test[["E"]],
                       design = design.test,
                       weights = voom.test[["weights"]])

eFDR.test <- mclapply(1:4,
                      function(i) {
                        t <- voom.fit.test[["coefficients"]][, i+1]/voom.fit.test[["stdev.unscaled"]][, i+1]/voom.fit.test[["sigma"]] # 1: intercept
                        p <- 2*pt(-abs(t), df = voom.fit.test[["df.residual"]])
                        return(qvalue(p)) },
                      mc.cores = 4L)

voom.DEG.test <- mclapply(1:4,
                          function(i) rownames(dat.expr.test)[ eFDR.test[[i]][["qvalues"]] < 0.05 ],
                          mc.cores = 4L)

names(eFDR.test) = names(voom.DEG.test) = vars.pool 

# Display the common DEGs between the training set and testing set identified by multivariate limma with voom weights
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = voom.DEG.train[[x]], Test = voom.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### edgeR (full model)
```{r DEG.compare.within.MultiedgeR.noTMM}
# Create the DGEList data class and then estimate the trended dispersions
t0 <- Sys.time()
y.train <- DGEList(counts = dat.expr.train, 
                   lib.size = colSums(dat.expr.train)) %>% 
             estimateGLMTrendedDisp(design.train)

# Estimate the quasi-likelihood (QL) dispersion
fit.train <- glmQLFit(y.train, design.train)

# Perform the hypothesis testing of QL dispersion
qlf.train <- mclapply(1:4,
                      function(i) glmQLFTest(fit.train, coef = i + 1), # coef: integer or character index vector indicating which coefficients of the linear model are to be tested equal to zero.
                      mc.cores = 4L)
t1 <- Sys.time()
t1 - t0

# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) qlf.train[[i]][["table"]][["PValue"]] %>%
                         qvalue(),
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
edgeR.DEG.train <- mclapply(1:4,
                            function(i) rownames(dat.expr.train)[ eFDR.train[[i]][["qvalues"]] < 0.05 ],
                            mc.cores = 4L)

names(qlf.train) = names(eFDR.train) = names(edgeR.DEG.train) = vars.pool

# Repeat the above steps for the testing data
y.test <- DGEList(counts = dat.expr.test, 
                  lib.size = colSums(dat.expr.test)) %>% 
            estimateGLMTrendedDisp(design.test)

fit.test <- glmQLFit(y.test, design.test)

qlf.test <- mclapply(1:4,
                    function(i) glmQLFTest(fit.test, coef = i + 1),
                    mc.cores = 4L)

eFDR.test <- mclapply(1:4,
                      function(i) qlf.test[[i]][["table"]][["PValue"]] %>% qvalue(),
                      mc.cores = 4L)

edgeR.DEG.test <- mclapply(1:4,
                           function(i) rownames(dat.expr.test)[ eFDR.test[[i]][["qvalues"]] < 0.05 ],
                           mc.cores = 4L)

names(qlf.test) = names(eFDR.test) = names(edgeR.DEG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate edgeR
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = edgeR.DEG.train[[x]], Test = edgeR.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### edgeR + TMM (full model)
```{r DEG.compare.within.MultiedgeR.TMM}
# Create the DGEList data class and then estimate the trended dispersions
t0 <- Sys.time()
y.train <- DGEList(counts = dat.expr.train, 
                   lib.size = colSums(dat.expr.train)) %>% 
             calcNormFactors() %>% 
             estimateGLMTrendedDisp(design.train)

# Estimate the quasi-likelihood (QL) dispersion
fit.train <- glmQLFit(y.train, design.train)

# Perform the hypothesis testing of QL dispersion
qlf.train <- mclapply(1:4,
                      function(i) glmQLFTest(fit.train, coef = i + 1), 
                      mc.cores = 4L)
t1 <- Sys.time()
t1 - t0

# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) qlf.train[[i]][["table"]][["PValue"]] %>%
                         qvalue(),
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
edgeR.DEG.train <- mclapply(1:4,
                            function(i) rownames(dat.expr.train)[ eFDR.train[[i]][["qvalues"]] < 0.05 ],
                            mc.cores = 4L)

names(qlf.train) = names(eFDR.train) = names(edgeR.DEG.train) = vars.pool

# Repeat the above steps for the testing data
y.test <- DGEList(counts = dat.expr.test, 
                  lib.size = colSums(dat.expr.test)) %>% 
            calcNormFactors() %>% 
            estimateGLMTrendedDisp(design.test)

fit.test <- glmQLFit(y.test, design.test)

qlf.test <- mclapply(1:4,
                    function(i) glmQLFTest(fit.test, coef = i + 1),
                    mc.cores = 4L)

eFDR.test <- mclapply(1:4,
                      function(i) qlf.test[[i]][["table"]][["PValue"]] %>% qvalue(),
                      mc.cores = 4L)

edgeR.DEG.test <- mclapply(1:4,
                           function(i) rownames(dat.expr.test)[ eFDR.test[[i]][["qvalues"]] < 0.05 ],
                           mc.cores = 4L)

names(qlf.test) = names(eFDR.test) = names(edgeR.DEG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate edgeR
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = edgeR.DEG.train[[x]], Test = edgeR.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### DESeq2 (full model)
```{r DEG.compare.within.MultiDESeq2.noTMM}
# Build the DESeqDataSet and then DESeq2 model for the training set
t0 <- Sys.time()
name.formula <- c("BMI_high_vs_low", "AGE_old_vs_young", "SEX_male_vs_female", "MHABNWBC_yes_vs_no") 
# These names can be obtained by running resultsNames(DESeq(dds))
# [1] "Intercept"          "BMI_high_vs_low"    "AGE_old_vs_young"  [4] "SEX_male_vs_female" "MHABNWBC_yes_vs_no"
dds <- DESeqDataSetFromMatrix(countData = cts.train, 
                              colData = coldata.train, 
                              design = ~BMI + AGE + SEX + MHABNWBC)

res.train <- mclapply(1:4, 
                      function(i) {
                        return(results(DESeq(dds), name = name.formula[i])) }, # name: extract individual effects
                      mc.cores = 4L)
t1 <- Sys.time()
t1 - t0


# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) qvalue(res.train[[i]][["pvalue"]])$qvalues,
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
DESeq2.DEG.train <- mclapply(1:4,
                             function(i) rownames(cts.train)[eFDR.train[[i]] < 0.05],
                             mc.cores = 4L)

names(res.train) = names(eFDR.train) = names(DESeq2.DEG.train) = vars.pool

# Repeat the above steps for the testing set
dds <- DESeqDataSetFromMatrix(countData = cts.test, 
                              colData = coldata.test, 
                              design = ~BMI + AGE + SEX + MHABNWBC)

res.test <- mclapply(1:4, 
                     function(i) {
                      return(results(DESeq(dds), name = name.formula[i])) },
                      mc.cores = 4L)

eFDR.test <- mclapply(1:4,
                      function(i) qvalue(res.test[[i]][["pvalue"]])$qvalues,
                      mc.cores = 4L)

DESeq2.DEG.test <- mclapply(1:4,
                            function(i) rownames(cts.test)[eFDR.test[[i]] < 0.05],
                            mc.cores = 4L)

names(res.test) = names(eFDR.test) = names(DESeq2.DEG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate DESeq2
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = DESeq2.DEG.train[[x]], Test = DESeq2.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```


##### DESeq2 + TMM (full model)
```{r DEG.compare.within.MultiDESeq2.TMM}
# Build the DESeqDataSet and then DESeq2 model for the training set
t0 <- Sys.time()
name.formula <- c("BMI_high_vs_low", "AGE_old_vs_young", "SEX_male_vs_female", "MHABNWBC_yes_vs_no") 
# Transform the TMM normalization factors to be used in DESeq2
lib.size <- colSums(cts.train)
norm.factor <- calcNormFactors(cts.train, method = "TMM")
size.factor <- lib.size*norm.factor/exp(mean(log(lib.size*norm.factor)))
dds <- DESeqDataSetFromMatrix(countData = cts.train, 
                              colData = coldata.train, 
                              design = ~BMI + AGE + SEX + MHABNWBC)
sizeFactors(dds) <- size.factor
res.train <- mclapply(1:4, 
                      function(i) {
                        return(results(DESeq(dds), name = name.formula[i])) }, # name: extract individual effects
                      mc.cores = 4L)
t1 <- Sys.time()
t1 - t0

# Estimate the FDR for each variable of interest
eFDR.train <- mclapply(1:4,
                       function(i) qvalue(res.train[[i]][["pvalue"]])$qvalues,
                       mc.cores = 4L)

# Output the Ensembl gene IDs of DEGs for each variable of interest
DESeq2.DEG.train <- mclapply(1:4,
                             function(i) rownames(cts.train)[eFDR.train[[i]] < 0.05],
                             mc.cores = 4L)

names(res.train) = names(eFDR.train) = names(DESeq2.DEG.train) = vars.pool

# Repeat the above steps for the testing set
lib.size <- colSums(cts.test)
norm.factor <- calcNormFactors(cts.test, method = "TMM")
size.factor <- lib.size*norm.factor/exp(mean(log(lib.size*norm.factor)))
dds <- DESeqDataSetFromMatrix(countData = cts.test, 
                              colData = coldata.test, 
                              design = ~BMI + AGE + SEX + MHABNWBC)
sizeFactors(dds) <- size.factor
res.test <- mclapply(1:4, 
                    function(i) {
                      return(results(DESeq(dds), name = name.formula[i])) }, # name: extract individual effects
                    mc.cores = 4L)

eFDR.test <- mclapply(1:4,
                      function(i) qvalue(res.test[[i]][["pvalue"]])$qvalues,
                      mc.cores = 4L)

DESeq2.DEG.test <- mclapply(1:4,
                            function(i) rownames(cts.test)[eFDR.test[[i]] < 0.05],
                            mc.cores = 4L)

names(res.test) = names(eFDR.test) = names(DESeq2.DEG.test) = vars.pool

# Display the common DEGs between the training set and testing set identified by multivariate DESeq2
plot.array <- mclapply(1:4,
                       function(x) {ggVennDiagram(list(Train = DESeq2.DEG.train[[x]], Test = DESeq2.DEG.test[[x]]), 
                                                  label_alpha = 0, label_color = "white") + 
                                      theme(legend.position = "none", plot.title = element_text(hjust = 0.5, colour = "red")) + 
                                      ggtitle(vars.pool[x]) },
                       mc.cores = 4L)
grid.arrange(do.call("arrangeGrob", c(plot.array, ncol = 4)))
```
