---
title: "Microcalcification Project"
author: "Anni Liu"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
knit: knitautomator::knit_filename
output:
  word_document:
    fig_caption: no
    fig_height: 4
    fig_width: 4
    highlight: null
    toc: yes
    reference_docx: manuscript_style_V0.docx
  html_document: default
params:
  date.analysis: !r format(Sys.Date(), "%Y%B%D")
  plot.fig: TRUE
  results.folder: FALSE
editor_options: 
  chunk_output_type: console
---


```{r shorcut, include=FALSE}
#################################################################
##                  RStudio keyboard shortcut                  ##
#################################################################
# Cursor at the beginning of a command line: Ctrl+A
# Cursor at the end of a command line: Ctrl+E
# Clear all the code from your console: Ctrl+L
# Create a pipe operator %>%: Ctrl+Shift+M (Windows) or Cmd+Shift+M (Mac)
# Create an assignment operator <-: Alt+- (Windows) or Option+-(Mac) 
# Knit a document (knitr): Ctrl+Shift+K (Windows) or Cmd+Shift+K (Mac)
# Comment or uncomment current selection: Ctrl+Shift+C (Windows) or Cmd+Shift+C (Mac)
```


```{r attach_lib_func, include=FALSE}
##################################################################
##                Attach libraries and functions                ##
##################################################################
# devtools::install("/Library/Frameworks/R.framework/Versions/4.2/Resources/library/BTKR")
easypackages::libraries("BTKR", "multcomp", "readxl", "tidyverse", "fst") |> suppressPackageStartupMessages()
"%_%" <- function(m, n) paste0(m, "_", n)
"%0%" <- function(m, n) paste0(m, n)
```


```{r global_options, include=FALSE}
#################################################################
##                          Automator                          ##
#################################################################
if (params$plot.fig) {
  dir.fig <- "../report/figs" %_% params$date.analysis %0% "/"
  # Need "/", otherwise, the images are saved directly under the report folder
  
  if (!dir.exists(dir.fig)) { 
    # If the figure directory does not exist, make a new directory under the folder report named with the date passed from the params$date.analysis in YAML
    dir.create(dir.fig) 
  }
  
  knitr::opts_chunk$set( # Setting parameters when figures are plotted
    fig.width = 4, fig.height = 4, 
    fig.path = dir.fig, dev = "png", dpi = 300,
    echo = FALSE, warning = FALSE, message = FALSE,
    cache = FALSE,
    comment = ""
  )
} else { # Setting parameters when figures are not plotted
  knitr::opts_chunk$set(
    echo = FALSE, warning = FALSE, message = FALSE,
    cache = FALSE,
    comment = ""
  )
}

if (params$results.folder) { # Suitable when the results need to be stored outside the MS word report
  dir.result <- "../report/results" %_% params$date.analysis
  
  if (!dir.exists(dir.result)) {
    # If the directory does not exist, make a new directory under the folder report named with the date passed from the params$date.analysis in YAML 
    
    dir.create(dir.result)
  }
}
```


# Data preparation
```{r, eval=FALSE}
# Clean data
dat.full <- readxl::read_xlsx(
  "../data/raw/Coded Microcalcs v6 offline.xlsx",
  sheet = "Coded",
  range = c("A1:AC122"),
  col_types = c(
    rep("numeric", 14),
    rep("date", 3),
    rep("numeric", 6),
    "text", # X21: Dorexcision: 3/23/2022; 4/13/22; 5/4/22
    rep("numeric", 2), 
    "date",
    "numeric",
    "text"
  ),
  col_names = TRUE,
  na = c("Unknown", "unknown", "N/A", "n/a")
) %>%
  rename(
    "StudyID" = "Record ID",
    "Insure.type" = "Insurance",
    "Age.Dx" = "Age_Diagnosis",
    "MMGSD" = "Mammo_Screen",
    "T.stage" = "cT",
    "N.stage" = "cN",
    "ER" = "ER status",
    "PR" = "PR status",
    "HER2" = "HER2 status",
    "PLM.plan" = "PLM_planned",
    "Tumor.type" = "Tumor Type",
    "Date.surg" = "DOS",
    "Date.PLM" = "DOPLM",
    "Date.rad" = "DORad",
    "Initial.margin" = "Intitial_margins",
    "Time.PLM.day" = "time to PLM (days)",
    "Timing.CTX" = "Timing_Chemotherapy",
    "PLM.calcs" = "PLM_calcs",
    "Time.rad.day" = "time to radiation (days)",
    "Reexcision" = "Re-exicion performed?",
    "Date.reex" = "Dorexcision",
    "Pathology.reex" = "Re-ex_path",
    "Surv.micalc" = "Surveillance_microcalcs",
    "Date.surv" = "Surveillance_date",
    "Time.surv.day" = "Time_to_Surveillance",
    "Comment" = "comments"
  ) %>%
  mutate(
    Race.2 = ifelse(Race == 5, NA, Race),
    Race.2 =
      factor(
        Race.2,
        levels = c(0, 1, 2, 3, 4),
        labels = c(
          "Asian",
          "Non-hispanic black",
          "Non-hispanic white",
          "Hispanic",
          "Other"
        ),
        ordered = TRUE
      )
  ) %>%
  mutate(Insure.type.2 = factor(
    Insure.type,
    levels = c(0, 1),
    labels = c("Private", "Medicare"),
    ordered = TRUE
  )) %>%
  mutate(MMGSD.2 = factor(
    MMGSD,
    levels = c(0, 1),
    labels = c("No", "Yes"),
    ordered = TRUE
  )) %>%
  mutate(T.stage.2 = factor(
    T.stage,
    levels = c(0, 1, 2, 3, 4, 5),
    labels = c("Tis", "T1a", "T1b", "T1c", "Tmic", "T2"),
    ordered = TRUE
  )) %>%
  mutate(N.stage.2 = factor(
    N.stage,
    levels = c(0, 1, 2),
    labels = c("N0", "N1", "N2"),
    ordered = TRUE
  )) %>%
  mutate(
    ER.2 = ifelse(ER == 2, NA, ER),
    ER.2 = factor(
      ER.2,
      levels = c(0, 1),
      labels = c("Negative", "Positive"),
      ordered = TRUE
    )
  ) %>%
  mutate(
    PR.2 = ifelse(PR == 2, NA, PR),
    PR.2 = factor(
      PR.2,
      levels = c(0, 1),
      labels = c("Negative", "Positive"),
      ordered = TRUE
    )
  )  %>%
  mutate(
    HER2.2 = ifelse(HER2 == 2, NA, HER2),
    HER2.2 = factor(
      HER2.2,
      levels = c(0, 1),
      labels = c("Negative", "Positive"),
      ordered = TRUE
    )
  ) %>%
  mutate(
    PLM.2 = ifelse(PLM == 2, NA, PLM),
    PLM.2 = factor(
      PLM.2,
      levels = c(0, 1),
      labels = c("No", "Yes"),
      ordered = TRUE
    )
  ) %>%
  mutate(
    PLM.plan.2 = ifelse(PLM.plan == 2, NA, PLM.plan),
    PLM.plan.2 = factor(
      PLM.plan.2,
      levels = c(0, 1),
      labels = c("No", "Yes"),
      ordered = TRUE
    )
  ) %>%
  mutate(
    Tumor.type.2 = factor(
    Tumor.type,
    levels = c(0, 1, 2, 3, 4, 5, 6, 7),
    labels = c(
      "DCIS",
      "LCIS",
      "IDC",
      "ILC",
      "IDC/DCIS",
      "ILC/DCIS",
      "Metaplastic carcinoma/DCIS",
      "Adenoid cystic carcinoma"
    ),
    ordered = TRUE
  )) %>%
  mutate(
    Initial.margin.2 = factor(
    Initial.margin,
    levels = c(0, 1, 2, 3, 4),
    labels = c(
      "Negative",
      "Positive",
      "Close",
      "NegativeCarcinomaCloseDCIS",
      "NegativeCarcinomaPositiveDCIS"
    ),
    ordered = TRUE
  )) %>%
  mutate(
    Initial.margin.3 = ifelse(Initial.margin.2 == "Negative", "Negative", "Positive/close"),
    Initial.margin.3 = factor(Initial.margin.3, 
                              levels = c("Negative", "Positive/close"),
                              ordered = TRUE)
  ) %>% 
  mutate(
    PLM.calcs.2 = ifelse(PLM.calcs == 2, NA, PLM.calcs),
    PLM.calcs.2 = factor(
      PLM.calcs.2,
      levels = c(0, 1),
      labels = c("No", "Yes"),
      ordered = TRUE
    )
  ) %>%
  mutate(
    Reexcision.2 = factor(
    Reexcision,
    levels = c(0, 1, 2),
    labels = c("No", "Yes", "Mastectomy"),
    ordered = TRUE
  )) %>% 
  mutate(
    Surv.micalc.2 = ifelse(Surv.micalc == 2, NA, Surv.micalc),
    Surv.micalc.2 = factor(Surv.micalc.2,
                           levels = c(0, 1),
                           labels = c("No", "Yes"))
  ) %>% 
  mutate(
    Pathology.reex.2 = factor(
    Pathology.reex,
    levels = c(0, 1, 2),
    labels = c("Negative", "DCIS", "Carcinoma"),
    ordered = TRUE
  )) %>% 
  mutate(
    Pathology.reex.3 = ifelse(Pathology.reex.2 == "Negative", "Negative", "DCIS/Carcinoma"),
    Pathology.reex.3 = factor(Pathology.reex.3, 
                              levels = c("Negative", "DCIS/Carcinoma"))
  ) %>%
  mutate(
    Timing.CTX.2 = ifelse(Timing.CTX == 3, NA, Timing.CTX),
    Timing.CTX.2 = factor(Timing.CTX.2, 
                          levels = c(0, 1, 2), 
                          labels = c("No chemo", "Before radiation", "After radiation"),
                          ordered = T)
  ) %>% 
  mutate(
    Time.PLM.day.2 = as.numeric(as.Date(Date.PLM) - as.Date(Date.surg))
  ) %>%
  mutate(
    Time.rad.day.2 = as.numeric(as.Date(Date.rad) - as.Date(Date.surg))
  ) %>%
  mutate(
    Time.surv.day.2 = as.numeric(as.Date(Date.surv) - as.Date(Date.surg))
  ) %>% 
  data.frame()

##------Check PLM and PLM.calcs of the records 57, 69, and 121------
dat.full[c(57, 69, 121), c("PLM.2", "PLM.calcs.2")]

##------Check the structure and distribution of factor/character variables------
all.fac <- sapply(names(dat.full)[sapply(dat.full, is.factor)], function(x) with(dat.full, table(get(x), useNA = "ifany")))  
# View(all.fac)

all.fac.lev <- sapply(names(all.fac), function(x) with(dat.full, levels(get(x))))  
# View(all.fac.lev)

all.char <- sapply(names(dat.full)[sapply(dat.full, is.character)], function(x) with(dat.full, table(get(x), useNA = "ifany")))  
# View(all.char)
```


```{r save_cleaned_data, eval=FALSE}
date.analysis <- format(Sys.Date(), "%Y%b%d")
write_fst(dat.full, path = paste0("../data/derived/", date.analysis, "_dat_microcalcs.RData"), compress = 50, uniform_encoding = TRUE)
write.csv(dat.full, paste0("../data/derived/", date.analysis, "_dat_microcalcs.csv"), row.names = F)
```


```{r save_load_processed_data}
dat.full <- read_fst(path = "../data/derived/2023May17_dat_microcalcs.RData")
```


```{r eval=FALSE, include=FALSE}
# VERIFY time from lumpectomy to PLM
idx <- with(dat.full, which(Time.PLM.day != Time.PLM.day.2))
dat.full[idx, c("Time.PLM.day", "Time.PLM.day.2")]
## Check if the missing is consistent
with(dat.full, setdiff(which(is.na(Time.PLM.day)), which(is.na(Time.PLM.day.2)))) 


# VERIFY time from lumpectomy to radiation,
idx <- with(dat.full, which(Time.rad.day != Time.rad.day.2))
dat.full[idx, c("Time.rad.day", "Time.rad.day.2")]
## Check if the missing is consistent
idx <- with(dat.full, setdiff(which(is.na(Time.rad.day)), which(is.na(Time.rad.day.2))))
dat.full[idx, c("Time.rad.day", "Time.rad.day.2")]


# VERIFY time from lumpectomy to surveillance
idx <- with(dat.full, which(Time.surv.day != Time.surv.day.2))
dat.full[idx, c("Time.surv.day", "Time.surv.day.2")]
## Check if the missing is consistent
with(dat.full, setdiff(which(is.na(Time.surv.day)), which(is.na(Time.surv.day.2))))
```
Notice that the `time to PLM (days)` of the column T in subjects (IDs: `r with(dat.full, which(Time.PLM.day != Time.PLM.day.2))`) should be changed into 28 and 34. The `time to radiation (days)` of the column V in subjects (IDs: `r c(with(dat.full, which(Time.rad.day != Time.rad.day.2)), with(dat.full, setdiff(which(is.na(Time.rad.day)), which(is.na(Time.rad.day.2)))))`) should be changed into 44, 40, 76, 42, 48, 36. The `time to surveillance (days)` of the column AB in subjects (IDs: `r with(dat.full, which(Time.surv.day != Time.surv.day.2))`) should be changed into 251, 270, 1461, 335, 203, 298.


```{r set_variables}
dat.work <- dat.full
vars.all <- c(
  "Race.2",
  "BMI",
  "Insure.type.2",
  "Age.Dx",
  "MMGSD.2",
  "T.stage.2",
  "N.stage.2",
  "ER.2",
  "PR.2",
  "HER2.2",
  "PLM.2",
  "PLM.plan.2",
  "Tumor.type.2",
  "Initial.margin.2",
  "Initial.margin.3",
  "PLM.calcs.2",
  "Reexcision.2", 
  "Pathology.reex.2",
  "Pathology.reex.3",
  "Surv.micalc.2",
  "Timing.CTX.2",
  "Time.PLM.day.2",
  "Time.rad.day.2",
  "Time.surv.day.2"
)

# Use 0 or 1 to indicate if the variable is continuous or categorical
vars.cat <- rep(1, length(vars.all))
vars.cat[vars.all %in% c("BMI", "Age.Dx", "Time.PLM.2", "Timing.CTX", "Time.PLM.day.2", "Time.rad.day.2", "Time.surv.day.2")] <- 0
```


# Methods of summary tables
The association between a categorical variable and a grouping variable (e.g., initial lumpectomy margins) is examined using the Fisher’s exact test. Difference in the value of a continuous variable among patients of different groups was examined using the Wilcoxon rank sum test (for two groups comparison) or Kruskal Wallis rank sum test (for more than two groups comparison). Notice that the p-value for the Wilcoxon rank sum test or Kruskal Wallis rank sum test is aligned with the median (IQR) summaries in a summary table. For variable with missing values, the difference in the proportion of missingness across different groups is also examined using the Fisher's exact test. All p values are two-sided. All statistical analyses are performed in R Version 4.2.3 (R Foundation for Statistical Computing, Vienna, Austria). The R packages "BTKR", "multcomp", "readxl", "tidyverse", and "fst" are used in this study. 


## Patients characteristics for all patients in the dataset
```{r, results="hide"}
out <- fsmry.dmgrph(
  dat = dat.work,
  vars = vars.all,
  vars.cat = vars.cat,
  by = NULL)
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by PLM for patients with available PLM information
```{r, results="hide"}
vars.cat.rm <- which(vars.all %in% c("PLM.2"))
out <- fsmry.dmgrph(
  dat = dat.work,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "PLM.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## *Patients characteristics by PLM for patients with available PLM information
```{r, results="hide"}
dat.work.1 <- dat.work[dat.work$Initial.margin.3 == "Positive/close", ]
vars.cat.rm <- which(vars.all %in% c("PLM.2"))
out <- fsmry.dmgrph(
  dat = dat.work.1,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "PLM.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by PLM for patients who do not receive chemotherapy before radiation
```{r, results="hide"}
dat.work.2 <- dat.work[which(dat.work$Timing.CTX.2 != "Before radiation"), ]
vars.cat.rm <- which(vars.all %in% c("PLM.2"))
out <- fsmry.dmgrph(
  dat = dat.work.2,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "PLM.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by initial lumpectomy margins (`Initial.margin.2`) for patients with completed PLM
```{r, results="hide"}
dat.work.3 <- dat.work[which(dat.work$PLM.2 == "Yes"), ]
vars.cat.rm <- which(vars.all %in% c("PLM.2", "Initial.margin.2", "Initial.margin.3"))
out <- fsmry.dmgrph(
  dat = dat.work.3,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "Initial.margin.2")
# Notice: Initial.margin.2 cannot contain the values that have the space; otherwise it will give the error message: "Error in wilcox.test.default(y1, y2, exact = F) : not enough (non-missing) 'x' observations"
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by initial lumpectomy margins (`Initial.margin.3`) for patients with completed PLM
```{r, results="hide"}
vars.cat.rm <- which(vars.all %in% c("PLM.2", "Initial.margin.2", "Initial.margin.3"))
out <- fsmry.dmgrph(
  dat = dat.work.3,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "Initial.margin.3")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## *Patients characteristics by initial lumpectomy margins (`Initial.margin.3`) for patients without PLM
```{r, results="hide"}
vars.cat.rm <- which(vars.all %in% c("PLM.2", "PLM.calcs.2", "Initial.margin.2", "Initial.margin.3", "Time.PLM.day.2"))
dat.work.3.1 <- dat.work[which(dat.work$PLM.2 == "No"), ]
out <- fsmry.dmgrph(
  dat = dat.work.3.1,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "Initial.margin.3")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by residual microcalcification (`PLM.calcs.2`) for patients with completed PLM
```{r, results="hide"}
vars.cat.rm <- which(vars.all %in% c("PLM.2", "PLM.calcs.2"))
out <- fsmry.dmgrph(
  dat = dat.work.3,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "PLM.calcs.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by initial lumpectomy margins (`Initial.margin.2`) for patients in re-excision surgery performed to resect residual microcalcifications
```{r, results="hide"}
dat.work.4 <- dat.work[which(dat.work$PLM.calcs.2 == "Yes" & dat.work$Reexcision.2 == "Yes"), ]

vars.cat.rm <- which(vars.all %in% c("Initial.margin.2", "Initial.margin.3", "Reexcision.2", "PLM.calcs.2", "PLM.2"))
out <- fsmry.dmgrph(
  dat = dat.work.4,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "Initial.margin.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Patients characteristics by initial lumpectomy margins (`Initial.margin.3`) for patients in re-excision surgery performed to resect residual microcalcifications
```{r, results="hide"}
dat.work.4 <- dat.work[which(dat.work$PLM.calcs.2 == "Yes" & dat.work$Reexcision.2 == "Yes"), ]

vars.cat.rm <- which(vars.all %in% c("Initial.margin.2", "Initial.margin.3", "Reexcision.2", "PLM.calcs.2", "PLM.2"))
out <- fsmry.dmgrph(
  dat = dat.work.4,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "Initial.margin.3")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Addition: patients characteristics by residual microcalcification (`PLM.calcs.2`) for patients who complete PLM but do not receive chemotherapy before radiation
```{r, results="hide"}
dat.work.5 <- dat.work[which(dat.work$Timing.CTX.2 != "Before radiation" & dat.work$PLM.2 == "Yes"), ]
vars.cat.rm <- which(vars.all %in% c("PLM.2", "PLM.calcs.2"))
out <- fsmry.dmgrph(
  dat = dat.work.5,
  vars = vars.all[-vars.cat.rm],
  vars.cat = vars.cat[-vars.cat.rm],
  by = "PLM.calcs.2")
```

```{r, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


# Session Info
```{r}
sessionInfo()
```

