---
title: "Reconstruction Project"
author: "Anni Liu"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
knit: knitautomator::knit_filename
output:
  word_document:
    fig_caption: no
    fig_height: 3
    fig_width: 4
    highlight: null
    toc: yes
    reference_docx: manuscript_style_recon_V0.docx
params:
  date.analysis: !r format(Sys.Date(), "%Y%b%d")
  plot.fig: TRUE
  results.folder: FALSE
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
## Attach libraries and functions
easypackages::libraries("tidyverse", "readxl", "gtsummary", "gt", "flextable", "stringi", "fst", "broom", "labelled", "data.table", "zeallot", "BTKR", "MASS") |> suppressPackageStartupMessages()
"%_%" <- function(m, n) paste0(m, "_", n)
"%0%" <- function(m, n) paste0(m, n)
"%+%" <- function(m) paste0(m, collapse = "+")
```


```{r global_options, include=F}
if (params$plot.fig) {
  dir.fig <- "../report/figs" %_% params$date.analysis %0% "/"
  # Need "/", otherwise, the images are saved directly under the report folder
  
  if (!dir.exists(dir.fig)) { 
    # If the figure directory does not exist, we create a new directory under the folder report using the name figs + current date passed from the params$date.analysis in YAML
    dir.create(dir.fig) 
  }
  
  knitr::opts_chunk$set( # Setting parameters when figures are plotted
    fig.width = 4, fig.height = 3, 
    fig.path = dir.fig, dev = "png", dpi = 300,
    echo = FALSE, warning = FALSE, message = FALSE,
    cache = FALSE,
    comment = ""
  )
} else { # Setting parameters when figures are not plotted
  knitr::opts_chunk$set(
    echo = FALSE, warning = FALSE, message = FALSE,
    cache = FALSE,
    comment = ""
  )
}

if (params$results.folder) { # Suitable when the results need to be stored outside the microsoft word report
  dir.result <- "../report/results" %_% params$date.analysis
  
  if (!dir.exists(dir.result)) {
    # If the directory does not exist, we create a new directory under the folder report using the name results + current date passed from the params$date.analysis in YAML 
    
    dir.create(dir.result)
  }
}
```


# Data preparations

```{r load_cleaned_data, eval=FALSE, include=FALSE}
data_full <- read_fst(path = "../data/derived/2023Jul17_data_recon.RData")
```

```{r eval=FALSE, include=FALSE}
##------Load raw dataset------
data_full <- read_xlsx("../data/raw/Mastectomy Recon Data_June_STATS_V2.xlsx", 
                       sheet = "Mastectomy 2017-2021 (stats)", 
                       range = c("A1:Y606"), 
                       col_names = T,
                       na = c("Unknown", "", "NA", "Not applicable ", "Not applicable", "Not aplicable", "n/a", "N/a", "N/A", "Unknown grade (not reported or unavailable)", "Unknown (not reported or unavailable)", "Unk", "unk"))

##------Format variable names into the unified style (e.g., Patient ID -> Patient.id)------
temp_name <- names(data_full)
temp_name <- sapply(strsplit(temp_name, split = "\\-|\\s|\\(|\\)|\\/|\\%|^the$|\\?|,"), function(x) paste(x[!x %in% c("", "-", "(", ")", "/", "%", "the", "?", ",")], collapse = ".")) # \\s means the literal space 
temp_name <- gsub('\"', "", temp_name) # "Smoker.use.\"current\".\"former\".or.\"never\""
temp_name <- gsub("$", ".", temp_name) # Race without any comma [vs Patient.ID]
temp_name <- sub("\\..*", ".", temp_name) %0% tolower(substring(temp_name, regexpr("*.\\.", temp_name) + 2))
temp_name <- gsub(".$", "", temp_name)
names(data_full) <- temp_name

##------Check the structure and distribution of character variables------
all_char <- sapply(names(data_full)[sapply(data_full, is.character)], function(x) with(data_full, table(get(x), useNA = "ifany")))  
# View(all_char)

##------Recode variables------
help(":=")
data_full <- as.data.table(data_full)
data_full[,Procedure.year:=factor(Procedure.year)]
data_full[,Race.1:=gsub("^chi", "Chi", 
                        gsub("^tai", "Tai", 
                             gsub("^tib", "Tib", 
                                  gsub("^jap", "Jap", Race))))]
data_full$Race.1 <- factor(data_full$Race.1)
levels(data_full$Race.1) <- fct_relevel(.f = levels(data_full$Race.1), "Other", after = Inf) |> levels()
table(data_full$Race.1, data_full$Race.2)
table(data_full$Race.2, data_full$Race.3)
data_full[,Race.2:=factor(Race.2, levels=c("East Asian", "South Asian", "Southeast Asian", "Asian Other", "White", "Black", "Hispanic", "Other"))]
data_full[,Race.3:=factor(Race.3, levels=c("Asian", "White", "Black", "Hispanic", "Other"))]
data_full[,Primary.language:=gsub("^ara", "Ara", 
                                  gsub("^kor", "Kor", 
                                       gsub("^por", "Por", 
                                            gsub("^rus", "Rus",
                                                 gsub("^spa", "Spa", Primary.language)))))]
data_full[,Primary.language:=factor(Primary.language)]
levels(data_full$Primary.language) <- fct_relevel(.f = levels(data_full$Primary.language), "Other", after = Inf) |> levels()
data_full[,Primary.language.english:=factor(Primary.language.english, levels=c("Yes", "No"))]
data_full[,Insurance:=factor(Insurance, levels=c("Medicare", "Medicaid", "Private"))]
data_full[,Smoke:=gsub("^c", "C",
                       gsub("^f", "F",
                            gsub("^n", "N", Smoker.use.current.former.or.never)))]
data_full[,Smoke:=factor(Smoke, levels=c("Never", "Former", "Current"))]
data_full[,Diagnosis:=factor(Diagnosis.dcis.idc.etc, 
                             labels=c("Atypia/in situ", "Invasive", "Prophylaxis/risk reducing"))]
data_full[,Diagnosis:=factor(Diagnosis, levels=c("Prophylaxis/risk reducing", "Atypia/in situ", "Invasive"))]
data_full[,Chemotherapy:=factor(Chemo.neoadjuvant.adjuvent.or.none, labels=c("Adjuvant", "Neoadjuvant", "None"))]
data_full[,Chemotherapy:=factor(Chemotherapy, levels=c("None", "Adjuvant", "Neoadjuvant"))]
data_full[,Endocrine.therapy:=factor(Endocrine.therapy, levels=c("Anastrazole", "Exemestane", "Letrozole", "Tamoxifen", "None"))]
data_full[,Radiation:=factor(Radiation, levels=c("No", "Yes"))]
data_full[,Surgeon.gender:=factor(Surgeon.gender, levels=c("Female", "Male"))]
data_full[,Language.concordance:=factor(Patient.physician.language.concordance, levels=c("Yes", "No"))]
data_full[,Surgery.type:=factor(Type.of.surgery, labels=c("Bilateral mastectomy", "Unilateral mastectomy"))]
data_full[,Surgery.type:=factor(Surgery.type, levels=c("Unilateral mastectomy", "Bilateral mastectomy"))]
data_full[,Bilateral.cancer:=factor(if.bilateral.mastectomy.bilateral.cancer, levels=c("No", "Yes"))]
data_full[,Bilateral.risk.reducing:=factor(if.bilateral.mastectomy.bilateral.risk.reducing, levels=c("No", "Yes"))]
data_full[,Plastics.referral:=factor(Plastics.referral, labels=c("No", "No", "Yes", "Yes"))]
data_full[,Plastics.referral:=factor(Plastics.referral, levels=c("No", "Yes"))]
data_full[,Reconstruction:=factor(Recon.yes.no, labels=c("No", "No", "Yes", "Yes"))]
data_full[,Reconstruction:=factor(Reconstruction, levels=c("No", "Yes"))]
data_full[,Reconstruction.type:=factor(If.recon.type, labels=c("Autologous", "Implant"))]
data_full[,Reconstruction.type:=factor(Reconstruction.type, levels=c("Implant", "Autologous"))]

##------Check the structure and distribution of new factor variables [! missing distribution]------
all_fac <- sapply(names(data_full)[sapply(data_full, is.factor)], function(x) with(data_full, table(get(x), useNA = "ifany")))
# View(all_fac)

all_fac_lev <- sapply(names(all_fac), function(x) with(data_full, levels(get(x))))
# View(all_fac_lev)
```

```{r save_cleaned_data, eval=FALSE, include=FALSE}
date.analysis <- format(Sys.Date(), "%Y%b%d")
write_fst(data_full, 
          path = paste0("../data/derived/", date.analysis, "_data_recon.RData"), 
          compress = 50, uniform_encoding = T)

write.csv(data_full, 
          file = paste0("../data/derived/", date.analysis, "_data_recon.csv"), 
          row.names = F)
```

```{r load_cleaned_data_again, include=FALSE}
data_full <- read_fst(path = "../data/derived/2023Jul17_data_recon.RData")
```


**Data dictionary**

* `Procedure.year`: year of undergoing the mastectomy
* `Age.at.diagnosis`: age at diagnosis (in years)
* `Race.1`: all types of races
* `Race.2`: racial status with categories: East Asian (reference); South Asian; Southeast Asian; Asian Other; White; Black; Hispanic; Other
* `Race.3`: racial status with categories: Asian (reference); White; Black; Hispanic; Other
* `Primary.language`: all types of patients' primary languages
* `Primary.language.english`: if a patient's primary language is English: Yes (reference); No
* `Language.concordance`: if a patient's primary language accords with a physician's speaking language: Yes (reference); No
* `Insurance`: type of insurance with categories: Medicare (reference); Medicaid; Private
* `BMI`: body mass index ($kg/m^2$)
* `Charlson.comorbidity.index`: Charlson comorbidity index
* `Smoke`: smoking status with categories: Never (reference); Former; Current
* `Diagnosis`: diagnosis status with categories: Prophylaxis/risk reducing (reference); Atypia/in situ; Invasive
* `Chemotherapy`: type of chemotherapy with categories: None (reference); Adjuvant; Neoadjuvant 
* `Endocrine.therapy`: type of endocrine therapy with categories: Anastrazole (reference); Exemestane; Letrozole; Tamoxifen; None
* `Radiation`:if a patient undergoes radiation therapy with categories: No (reference); Yes
* `Surgeon.gender`: surgeon gender with categories: Female (reference); Male
* `Surgery.type`: type of surgery with categories: Unilateral mastectomy (reference); Bilateral mastectomy
* `Bilateral.cancer`: if a patient undergoes the bilateral mastectomy to remove cancer: No (reference); Yes
* `Bilateral.risk.reducing`: if a patient undergoes the bilateral mastectomy to reduce the risk: No (reference); Yes
* `Plastics referral`: if a patient is referred to plastic surgery: No (reference); Yes
* `Reconstruction`: any reconstruction with categories: No (reference); Yes
* `Reconstruction.type`: type of reconstruction with categories: Implant (reference); Autologous

# Summary tables
## Overall distributions of patient variables
```{r include=FALSE, results="hide"}
##------Set study variables for BTKR package------
var_all <- c("Procedure.year",
             "Age.at.diagnosis",
             "Race.1",
             "Race.2",
             "Race.3",
             "Primary.language",
             "Primary.language.english",
             "Language.concordance",
             "Insurance",
             "BMI",
             "Charlson.comorbidity.index",
             "Smoke",
             "Diagnosis",
             "Chemotherapy",
             "Endocrine.therapy",
             "Radiation",
             "Surgeon.gender",
             "Surgery.type",
             "Bilateral.cancer",
             "Bilateral.risk.reducing",
             "Plastics.referral",
             "Reconstruction",
             "Reconstruction.type"
             )

# Create an indicator [0, 1] for all categorical variables 
var_cat <- rep(x = 1, times = length(var_all))
var_cat[var_all %in% names(data_full)[sapply(data_full, is.numeric)]] <- 0
```


```{r echo=FALSE, results="hide"}
out <- fsmry.dmgrph(dat = data_full,
                    vars = var_all,
                    vars.cat = var_cat,
                    by = NULL)
```


```{r echo=FALSE, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Characteristics of the study population (publication-ready table)
```{r echo=FALSE, warning=FALSE}
var_focus <- c(
  "Age.at.diagnosis",
  "Race.2",
  "Race.3",
  "Primary.language",
  "Primary.language.english",
  "Language.concordance",
  "Insurance",
  "BMI",
  "Charlson.comorbidity.index",
  "Smoke",
  "Diagnosis",
  "Chemotherapy",
  "Endocrine.therapy",
  "Radiation",
  "Surgeon.gender",
  "Surgery.type",
  "Bilateral.cancer",
  "Bilateral.risk.reducing",
  "Plastics.referral",
  "Reconstruction",
  "Reconstruction.type"
)

var_label(data_full) <- list(
  Age.at.diagnosis = "Age at diagnosis (years)",
  Race.2 = "Race",
  Race.3 = "Race",
  Primary.language = "Patient's primary language",
  Primary.language.english = "English as the patient's primary language",
  Language.concordance = "Patient-physician language concordance",
  Insurance = "Type of insurance",
  BMI = "Body mass index (kg/m2)",
  Charlson.comorbidity.index = "Charlson Comorbidity Index",
  Smoke = "Smoking status",
  Diagnosis = "Diagnosis",
  Chemotherapy = "Type of chemotherapy",
  Endocrine.therapy = "Type of endocrine therapy",
  Radiation = "Type of radiation",
  Surgeon.gender = "Surgeon gender",
  Surgery.type = "Type of surgery",
  Bilateral.cancer = "Bilateral mastectomy to remove cancer",
  Bilateral.risk.reducing = "Bilateral mastectomy to reduce risk",
  Plastics.referral = "Plastics referral",
  Reconstruction = "Any reconstruction",
  Reconstruction.type = "Type of reconstruction"
)

tbl_summary(data = data_full |> dplyr::select(var_focus), 
            by = NULL,
            type = c(all_continuous() ~ "continuous2", # "continuous2" summaries are shown on 2 or more rows
                     all_dichotomous() ~ "categorical"),
            missing = "ifany",
            statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})",
                                                  "{mean} ± {sd}",
                                                  "{min}-{max}"))) |>
  modify_header(update = all_stat_cols() ~ "n = {n} \n n (%)") |>
  modify_table_body(
    dplyr::mutate, 
    label = case_when(label == "N missing" ~ "Unknown",
                      label == "Minimum-Maximum" ~ "Range",
                      T ~ label)) |>
  modify_footnote(update = everything() ~ NA) |> # Remove unnecessary footnotes
  bold_labels() |>
  as_flex_table() |>
  bold(bold = T, part = "header") |>
  mk_par(part = "body", i = 44, j = "label",
         value = as_paragraph("Body mass index (kg/m", as_sup("2"), ")"))
```


## Characteristics of patients stratified by whether postmastectomy breast reconstruction was performed (column percentage)
```{r echo=FALSE, results="hide"}
var.idx.rm <- Position(f = function(i) {i == "Reconstruction"} , x = var_all) 
out <- fsmry.dmgrph(dat = data_full,
                    vars = var_all[-var.idx.rm],
                    vars.cat = var_cat[-var.idx.rm],
                    by = "Reconstruction")
```


```{r echo=FALSE, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Characteristics of patients stratified by whether postmastectomy breast reconstruction was performed (row percentage)
```{r echo=FALSE, results="hide"}
# Examine the reconstruction rate for each category level
out <- fsmry.dmgrph(dat = data_full,
                    vars = var_all[-var.idx.rm],
                    vars.cat = var_cat[-var.idx.rm],
                    by = "Reconstruction",
                    prop.by.row = T)
```


```{r echo=FALSE, results="asis"}
knitr::kable(out[[1]], row.names = F)
```


## Characteristics of patients stratified by whether postmastectomy breast reconstruction was performed (publication-ready table)
```{r echo=FALSE, warning=FALSE}
data_full_2 <- data_full
data_full_2$Reconstruction <- factor(data_full_2$Reconstruction, labels = c("No reconstruction", "Reconstruction")) |> relevel("Reconstruction")
tbl_summary(data = data_full_2 |> dplyr::select(var_focus), 
            by = Reconstruction,
            type = c(all_continuous() ~ "continuous2",
                     all_dichotomous() ~ "categorical"),
            missing = "ifany",
            statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})",
                                                  "{mean} ± {sd}",
                                                  "{min}-{max}"))) |>
  modify_header(update = all_stat_cols() ~ "**{level}** \n (n = {n}) \n n (%)") |>
  modify_table_body(
    dplyr::mutate, 
    label = case_when(label == "N missing" ~ "Unknown",
                      label == "Minimum-Maximum" ~ "Range",
                      T ~ label)) |>
  modify_footnote(update = everything() ~ NA) |>
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T, B = 5000)) |>
  bold_labels() |>
  as_flex_table() |>
  bold(bold = T, part = "header") |> 
  mk_par(part = "body", i = 50, j = "label",
         value = as_paragraph("Body mass index (kg/m", as_sup("2"), ")"))
```


## Univariable logistic regression analyses of patient factors associated with reconstruction in all patients
```{r echo=FALSE, warning=FALSE}
data_full$Plastics.referral <- factor(data_full$Plastics.referral, levels = c("Yes", "No")) # If set "No" as the reference level, the estimate will be extremely large and the table was stretched very wide
data_full$Primary.language <- relevel(data_full$Primary.language, ref = "English")
data_full$Diagnosis <- factor(data_full$Diagnosis, levels = c("Invasive", "Atypia/in situ", "Prophylaxis/risk reducing")) # Use invasive as the reference category

var_label(data_full) <- list(
  Plastics.referral = "Plastics referral",
  Primary.language = "Patient's primary language")

t_uv <- tbl_uvregression(
  data = data_full[var_focus],
  method = glm,
  y = Reconstruction,
  method.args = list(family = binomial),
  exponentiate = T
) |> 
  bold_labels() |>
  as_flex_table() |>
  bold(bold = T, part = "header") |> 
  mk_par(part = "body", i = 46, j = "label",
         value = as_paragraph("Body mass index (kg/m", as_sup("2"), ")"))
t_uv
```


## Multivariable backward stepwise selection logistic regression analyses of patient factors associated with reconstruction
The backward stepwise logistic regression is used to estimate the independent effects of factors predictive of reconstruction. The full model includes the candidate predictors which are `Age.at.diagnosis`, `Race.2`, `Primary.language.english`, `Language.concordance`, `Insurance`, `BMI`, `Charlson.comorbidity.index`, `Smoke`, `Diagnosis`, `Surgeon.gender`, `Surgery.type`, `Plastics.referral`.
```{r echo=FALSE, warning=FALSE}
covariates <- var_focus[-which(var_focus %in% c("Race.3", "Chemotherapy", "Primary.language", "Endocrine.therapy", "Radiation", "Bilateral.cancer", "Bilateral.risk.reducing", "Reconstruction.type", "Reconstruction"))]
response <- "Reconstruction"

# "Plastics.referral"
# "Diagnosis"

data_full_3 <- na.omit(data_full[c("Patient.id", covariates, response)])

var_label(data_full_3) <- list(
  Age.at.diagnosis = "Age at diagnosis (years)",
  Race.2 = "Race",
  # Race.3 = "Race",
  # Primary.language = "Patient's primary language",
  Primary.language.english = "English as the patient's primary language",
  Language.concordance = "Patient-physician language concordance",
  Insurance = "Type of insurance",
  BMI = "Body mass index (kg/m2)",
  Charlson.comorbidity.index = "Charlson Comorbidity Index",
  Smoke = "Smoking status",
  Surgeon.gender = "Surgeon gender",
  Surgery.type = "Type of surgery",
  Reconstruction = "Any reconstruction",
  Plastics.referral = "Plastics referral"
)

glm.fit <- glm("%0%"(response%0%"~", "%+%"(covariates)), 
               data = data_full_3, family = binomial)
full.model <- glm.fit
min.model <- glm("%0%"(response%0%"~", "%+%"(c("Age.at.diagnosis", "Race.2"))), 
                 data = data_full_3, family = binomial)

glm.fit.back <- stepAIC(object = full.model,
                        direction = "backward", 
                        scope = list(upper = full.model,
                                     lower = min.model),
                        trace = 0)

t_mv <- tbl_regression(x = glm.fit.back, 
                       exponentiate = T,
                       pvalue_fun = function(x) style_pvalue(x, digits = 3),
                       add_estimate_to_reference_rows = T) |>
  add_n() |> 
  bold_labels() |>
  as_flex_table() |>
  bold(bold = T, part = "header")
t_mv
```

## Assess the multicollinearity via variance inflation factor
```{r echo=FALSE, results='asis'}
car::vif(glm.fit.back) |> knitr::kable()
```


## Univariable and multivariable logistic regression analyses of patient factors associated with reconstruction (publication-ready table)
Notice that both the univariable logistic regression results and multivariable backward stepwise selection logistic regression results are obtained from the study population of the same size, that is, 601.
```{r echo=FALSE, warning=FALSE}
t_uv_2 <- tbl_uvregression(
  data = data_full_3[c(covariates, response)], # Here use data_full_3
  method = glm,
  y = Reconstruction,
  method.args = list(family = binomial),
  exponentiate = T,
  hide_n = T,
  add_estimate_to_reference_rows = T
)

t_mv_2 <- tbl_regression(x = glm.fit.back, 
                         exponentiate = T,
                         pvalue_fun = function(x) style_pvalue(x, digits = 3),
                         add_estimate_to_reference_rows = T) |>
  bold_labels() 

t_merge <- tbl_merge(tbls = list(t_uv_2, t_mv_2),
                     tab_spanner = c("**Univariable analysis**", "**Multivariable analysis**"))

# t_merge[["table_styling"]][["header"]][["column"]]

t_merge |> 
  as_flex_table() |>
  mk_par(part = "body", i = 22, j = "label",
         value = as_paragraph("Body mass index (kg/m", as_sup("2"), ")")) |>
  width(width = 3, unit = "cm")
```


# Trend of the postmastectomy reconstruction rate over time (added with exact 95% confidence intervals)
```{r echo=FALSE, warning=FALSE, fig.height = 3, fig.width = 4, out.height=287.5399361022364, out.width=383.69304556354916}
line_plot_data <- dplyr::count(data_full, Procedure.year, Reconstruction)
Reconstruction_count <- line_plot_data$n
Reconstruction_rate <- Reconstruction_count[c(F, T)] / dplyr::count(data_full, Procedure.year)[["n"]]

# Estimate the 95% confidence interval using the exact method
r <- binom.confint(x = Reconstruction_count[c(F, T)], n = dplyr::count(data_full, Procedure.year)[["n"]], conf.level = 0.95, methods = "exact")

Reconstruction_data <- data.frame(Year = line_plot_data$Procedure.year |> unique(), Reconstruction_rate = Reconstruction_rate, Lower = r$lower, Upper = r$upper)

ggplot(data = Reconstruction_data, 
       mapping = aes(x = Year, y = Reconstruction_rate)) +
  geom_line(aes(group = 1), color = "steelblue2") +
  geom_ribbon(aes(x = 1:length(Year), ymin = Lower, ymax = Upper), linetype = 2, alpha = 0.1) + 
  theme_minimal() + 
  labs(y = "Reconstruction Rate", x = "Year") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0, 0.6)) +
  theme(legend.position = "none",
        axis.text = element_text(color = "black"),
        panel.grid.major.y = element_line(linewidth = 0.7), # Adjust the horizontal grid line
        panel.grid.minor.y = element_line(linewidth = 0.7),
        panel.grid.major.x = element_blank() # Remove the vertical grid lines
  )
```


# Trend of the postmastectomy reconstruction rate over time (added with Agresti-Coull 95% confidence intervals)
```{r echo=FALSE, warning=FALSE, fig.height = 3, fig.width = 4, out.height=287.5399361022364, out.width=383.69304556354916}
# Estimate the 95% confidence interval using the Agresti-Coull method
r <- binom.confint(x = Reconstruction_count[c(F, T)], n = dplyr::count(data_full, Procedure.year)[["n"]], conf.level = 0.95, methods = "ac")

Reconstruction_data <- data.frame(Year = line_plot_data$Procedure.year |> unique(), Reconstruction_rate = Reconstruction_rate, Lower = r$lower, Upper = r$upper)

ggplot(data = Reconstruction_data, 
       mapping = aes(x = Year, y = Reconstruction_rate)) +
  geom_line(aes(group = 1), color = "steelblue2") +
  geom_ribbon(aes(x = 1:length(Year), ymin = Lower, ymax = Upper), linetype = 2, alpha = 0.1) + 
  theme_minimal() + 
  labs(y = "Reconstruction Rate", x = "Year") + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0, 0.6)) +
  theme(legend.position = "none",
        axis.text = element_text(color = "black"),
        panel.grid.major.y = element_line(linewidth = 0.7), # Adjust the horizontal grid line
        panel.grid.minor.y = element_line(linewidth = 0.7),
        panel.grid.major.x = element_blank() # Remove the vertical grid lines
  )
```

# Session information
```{r}
sessionInfo()
```
